Approximation as Differentiation notes

### 2025-02-21 notes.tex
Two different functors..
Some progress.
Some attempt to make sense of Grothendieck construction when F is contravariant.
Setoid.
CMon.
Biproducts.
Some references.
Products (or coproducts) are enough to derive biproducts in a CMon-enriched category.

@@

Some of the key constructions:
\begin{itemize}
\item Category of families $\Fam$
\item Category of $\LatGal$ of bounded lattices and Galois connections
\end{itemize}

\noindent $\Set$ will often be $\Setoid$ in the Agda implementation but will gloss that here.

\input{notes/definitions}
\input{notes/language}

>>>>

\usepackage{bbm}
\usepackage{tikz-cd}

@@

Some of the key constructions:
\begin{itemize}
\item Category of families $\Fam(C)$ for any category $C$
\item Category of $\LatGal$ of bounded lattices and Galois connections
\end{itemize}

Is one of the goals to define sufficient conditions on $C$ for $\Fam(C)$ to be Cartesian closed?

\noindent $\Set$ will often be $\Setoid$ in the Agda implementation but I'm glossing that detail here.

\input{notes/definitions}
% \input{notes/language}

\section{Some references}

\cite{karvonen2020}

\bibliographystyle{plainnat}
\bibliography{bib}

### 2025-02-21 notes/definitions.tex
Biproducts.
Products (or coproducts) are enough to derive biproducts in a CMon-enriched category.

A category is $\CMon$-enriched if $\Hom{A}{B}$ is closed under the \emph{zero} morphism $\zero_{A,B}$ and
addition of morphisms $+_{A,B}$ satisfying the commutative monoid laws.

@@

>>>>

A category is $\CMon$-enriched if every $\Hom{A}{B}$ is a commutative monoid with the \emph{zero} morphism
$\zero_{A,B}$ and addition of morphisms $+_{A,B}$ as the commutative monoid operations, and composition
is a commutative monoid homomorphism.

\begin{proposition}
Suppose $C$ a $\CMon$-enriched monoidal category.
\begin{itemize}
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}

If $C$ is $\CMon$-enriched then any functor category $\Func{D}{C}$ is $\CMon$-enriched.

@@

Any category with biproducts has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A \oplus
B, i_A, i_B)$.
